An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Partial pass on App D

\cite{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.

@@

	It is just left to show (iii).
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
	Moreover, by $(ii)$, define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
Suppose $\V$ is a finite set $\V \subset \reals_+^\Y$.
Throughout, we will work with a function $g_\V$ generated by $\V$ of the following form.

\begin{definition}\label{def:g-finite}
  Define the function $g_\V : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}

@@

  $\implies$
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

%Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
\jessiet{Claim vs lemma?}
\begin{claim}\label{claim:G-intersection-H}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
  Then $G = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{lemma}\label{lem:G-full-dimensional}
  Given a finite, nonempty set $\V \subset \reals^d$ and $G := \hyp(g_\V)$, $G$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{lemma}
\begin{proof}
  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

This result, in conjunction with Theorem~\ref{thm:polyhedron-uniquely-gen-facets} yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$ and $G := \hyp(g_\V)$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = G \cap H$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
\end{proof}

@@

\begin{lemma}\label{lem:HY-subset-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
  $\H_\Y \subseteq \H^*$.
\end{lemma}
\begin{proof}
  If there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g_\V$ is finite at $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g_\V$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $\H^* = \{H^+\}$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$.

%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
\end{proof}

\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
  Let $\V \subset \reals^\Y_+$ be a finite set such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt. $\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.  
  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V'}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V'$.
\end{proof}

@@

\begin{assumption}\label{assum:V-star-exists-finite}
	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ such that $\hyp(g_\V) = \cap \H^*$.
	Moreover, $\V^* \subseteq \V$ is the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
\end{assumption}

@@

In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
Now suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.

%As before, take $G$ to be the hypograph of $g$.
We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$, and consider $g_\V$.  
Unlike \S~\ref{appsubsec:phase1}, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\V := L(\R)$ and $\H = \H_\Y \cup \H_{\V}$.
	Then $\hyp(g_\V) = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_\V)
	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_\V=\risk L_+$ for $x \in \reals^\Y_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$}~.  
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
\end{proof}

\jessie{I think we want to spell a little more out here before jumping to this corollary?}
\begin{corollary}
	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq \V := L(\R)$ such that \jessie{Check} $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
\end{corollary}

@@

\jessie{Which parts of these two do we want? another assumption commented out.  I think current one is more than sufficient}
\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function with $\V = L(\R)$.
	Moreover, $\risk \L_+ = g_\V$ is polyhedral.
	Finally, $\V^* \subseteq \V$ is a (unique) finite irredundant set such that $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
\end{assumption}

@@

\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
Throughout this section, suppose that we are given a set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
Moreover, we denote the unique irredundant set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
This is often established by Assumptions~\ref{assum:V-star-exists-finite} and \ref{assum:V-star-exists-infinite}.
We now consider projections from $\reals^d = \reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

\begin{claim}\label{claim:vstar-supporting-G}
	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
\end{claim}
\begin{proof}
	% \jessie{Notes in meeting:
	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
	%   Argue $G \subseteq H^+_{v^*}$ by definition.
	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
	%
	By assumption, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
	In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
	By definition of $g_\V$, we have $g_\V(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
\end{proof}

We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
This projected faces generated by $\V^*$ covers the nonnegative orthant.

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For each $v \in \V^*$, let $F_v = H_v \cap \hyp(g_\V^*)$. \jessiet{redundant?}
	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
\end{corollary}

@@

Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g$ for any $v \in \V$.

@@

	$\impliedby$
	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

>>>>

\citet{gallier2008notes} shows that every polyhedron $P$ has a unique and irredundant halfspace representation $\H^*$, and each $H^+ \in \H^*$ generates a facet of $P$.

@@

	It is just left to show (iii).
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
For now, we consider some $\V \subset \reals_+^\Y$.
Throughout, we will work with a function $g_\V$ generated by $\V$ of the following form.

\begin{definition}\label{def:g-finite}
  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}

@@

  $\implies$
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H^+_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

%Throughout this section let $G:= \hyp(g_\V)$ for a fixed finite set $\V$.
To start, we will assume $\V \subset \reals^\Y_+$ is finite.
Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
\jessiet{Claim vs lemma?}
\begin{claim}\label{claim:G-intersection-H}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  Then $\hyp(g_\V) = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{lemma}\label{lem:G-full-dimensional}
  Given a finite, nonempty set $\V \subset \reals^d$, $\hyp(g_\V)$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.} 
\end{lemma}
\begin{proof}
  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

This result allows us to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}, which yields a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $F = \hyp(g_\V) \cap H$ is a facet. 
\end{lemma}
\begin{proof}
  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i).
\end{proof}

@@

\begin{lemma}\label{lem:HY-subset-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, consider the unique finite set $\H^*$ as given by Lemma~\ref{lem:G-unique-facets-Hstar}. % such that $\hyp(g_\V) = \cap \H^*$ and $\H^* \subseteq (\H_\V \cup \H_\Y)$.
  $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
  If there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g_\V$ is finite at $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g_\V$ since $\V$ is finite including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $\H^* = \{H^+\}$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:HY-subset-Hstar}.
  ($\V^*$ is unique as halfspaces are uniquely determined.)
  Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
\end{proof}

\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
  Let $\V \subset \reals^\Y_+$ be a finite set, and $\V^*$ the unique finite set from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}. %such that $\H := \H_\Y \cup \H_{\V}$ satisfies $\hyp(g_{\V}) = \cap \H$, and take $\V^*$ the unique set such that irredundant (wrt. $\hyp(g_\V)$) set $\H^* = \H_\Y \cup \H_{\V^*}$.  
  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V'}$ by Lemma~\ref{lem:HY-subset-Hstar}, ergo $\V^* \subseteq \V'$.
\end{proof}

@@

\begin{assumption}\label{assum:V-star-exists-finite}
	Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ from Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $\hyp(g_\V) = \cap \H^*$.
	Moreover, $\V^* \subseteq \V$ is the unique finite set from Corollary~\ref{cor:anything-gen-G-subset-Hstar} such that $\H^* = \H_\Y \cup \H_{\V^*}$ is irredundant.
\end{assumption}

@@

In \S~\ref{appsubsec:phase1}, we discussed the function $g_\V$, where $\V \subset \reals^\Y_+$ was finite, but we move towards considering an infinite $\V$ in some settings relevant to embeddings.
Now suppose $L : \R \to \reals^\Y_+$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$, which we assume is polyhedral throughout.

%As before, take $G$ to be the hypograph of $g$.
We now define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$, and consider $g_\V$.  
Unlike \S~\ref{appsubsec:phase1}, $\V$ and $\H_\V$ could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}\label{claim:gV-equals-riskL}
	Given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$, consider $\V := L(\R)$ and $\H = \H_\Y \cup \H_{\V}$.
	Then $\hyp(g_\V) = \cap\H$.
	Moreover, there is a finite $\V' \subseteq \V$ such that $\hyp(g_\V) = \cap (\H_{\V'} \cup \H_\Y) = \hyp(g_{\V'})$ and $g_\V = g_{\V'}$. 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_\V)
	&\iff g_\V(x) \geq c & \text{ Definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_\V=\risk L_+$ for $x \in \reals^\Y_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in \V & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$}~.  
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $\hyp(g_\V) = \cap \H$.
	The existence of a finite $\V' \subseteq \V$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition.
	Finally, $\hyp(\risk L_+) = \hyp(g_\V) = \hyp(g_{\V'})$ if and only if $\risk L_+ = g_\V = g_{\V'}$. \jessiet{Omitting details on why $\V' \subseteq \V$.}
\end{proof}

\begin{corollary}
	Given minimizable $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a (unique) finite $\V^* \subseteq \V := L(\R)$ such that \jessie{Check} $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
\end{corollary}

@@

\jessie{Which parts of these two do we want? another assumption commented out.  I think current one is more than sufficient}
\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function with $\V = L(\R)$.
	Moreover, $\risk L_+ = g_\V$ is polyhedral.
	%$\V' \subseteq \V$ is a finite set such that $g_\V = g_{\V'}$.
	Finally, $\V^* \subseteq \V$ is a (unique) finite irredundant set such that $g_\V = g_{\V^*}$ and $\hyp(g_\V) = \hyp(g_{\V^*}) = \cap_{v \in \V^*} H^+_v \bigcap \cap_{y \in \Y} H^+_y = \cap(\H_{\V^*} \cup \H_\Y)$ is irredundant.
\end{assumption}
Observe that we can use $\V'$ from Claim~\ref{claim:gV-equals-riskL} to apply results from the finitely generated polyhedra case in \S~\ref{appsubsec:phase1}, in particular \ref{lem:G-unique-facets-Hstar}, and \ref{lem:HY-subset-Hstar}, and  Corollaries~\ref{cor:unique-set-loss-vectors-defining-facets} and \ref{cor:anything-gen-G-subset-Hstar} to justify the assumption of $\V^* \subseteq \V' \subseteq \V$.
However, once we have $\V^*$ via Assumption~\ref{assum:V-star-exists-infinite}, this set $\V^*$ also suffices to apply these statements.

@@

\subsection{Projecting from $\reals^d_+$ to $\reals^\Y_+$}\label{subsec:project-pi}
Throughout this section, suppose that we are given a set $\V$ such that $\hyp(g_\V)$ is a polyhedron. 
Moreover, we denote the unique irredundant finite set $\V^* \subseteq \V$ such that $g_\V = g_{\V^*}$.
This is often established by Assumptions~\ref{assum:V-star-exists-finite} and \ref{assum:V-star-exists-infinite}.
We now consider projections from $\reals^d = \reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

\begin{claim}\label{claim:vstar-supporting-G}
	Given $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, for all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $\hyp(g_\V)$ at $(x,g_\V(x))$.
\end{claim}
\begin{proof}
	% \jessie{Notes in meeting:
	%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
	%   Argue $G \subseteq H^+_{v^*}$ by definition.
	%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
	%
	By assumption, we have $g_\V(x) = g_{\V^*}(x) = \inf_{v \in \V^*}\inprod{v}{x} = \min_{v \in \V^*}\inprod{v}{x}$ for $x \in \reals^\Y_+$.
	In particular, consider a normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that the hyperplane $H_{v^*}$ such that $H_{v^*} = \partial H^+_{v^*}$ supports $\hyp(g_\V)$ at $(x,g(x))$.
	First, $\hyp(g_\V) \subseteq H^+_{v^*}$ by definition of $\hyp(g_\V)$ as the intersection of halfspaces including $H^+_{v^*}$.
	Thus, it is just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap \hyp(g_\V)$.
	%Recall from \S~\ref{appsubsec:notation} that $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
	By definition of $g_\V$, we have $g_\V(x)= g_{\V^*}(x) = \inprod{v^*}{x}$, so $(x,g_\V(x)) \in H_{v^*}$.
	Moreover, $(x,g_\V(x)) \in \hyp(g_\V) = \{(x,c) \mid g_\V(x) \geq c\}$ trivially since $g_\V(x) \geq g_\V(x)$.
\end{proof}

We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
This projected faces generated by $\V^*$ cover the nonnegative orthant.

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
	Then $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
\end{corollary}

@@

Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in \V$.

@@

	($\impliedby$)
	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
